### 2020-07-17 article.tex
PCBDDC unknowns

It is discretized using first order N\'ed\'elec finite elements and the \pk{PCBDDC} solver
is automatically customized to obtain a stable method with these elements~\cite{zampini2017balancing}.

@@

second level, new subdomains are built by aggregating the coarse element matrices of

>>>>

It is discretized using first order N\'ed\'elec finite elements and \pk{PCBDDC}
is automatically customized to obtain a stable method with these
elements~\cite{zampini2017balancing}. The number of unknowns is $\pgfmathprintnumber{5.6} \times 10^6$.

@@

second level with 16${,}$284 unknowns, new subdomains are built by aggregating the coarse element matrices of
